Responses to Reviews

### 2016-07-11 RMS/responses.tex
first version of 2nd revision is complete

\section{General Response}
We thank all the reviewers for their careful considerations on our
paper. The comments are very insightful and invaluable. Thanks to the
comments, we have improved the paper a lot to make it clearer and
better presented.

The main changes in the paper are as following, which we have also
highlighted in the revised manuscript:
\begin{itemize}
\item
Section~IV about the formal model of the target implementation is
revised. Some technical details have been simplified and more literal
explanations are used to deliver our ideas.

\item
Section~V.B is expanded. Some discussion on the efficiency of our
approach is added.

\item 
The detailed technical proof of Theorem~2 in Section~V.C has been
included in the Appendix.

\item
Section~VI about related work has been improved. 
\end{itemize}

Detailed responses to all the comments are shown in the rest of this
document.

@@

Thank you for the approval.

@@

@@

Yes, they are also terms. This is specified now.

@@

Thanks for pointing this out. Actually some of the timed operators are
used in Section V.A when describing the properties we verify. This
little problem is addressed now. We now only mention the necessary
timed operators which will be used, and also add explanations when
using them in Section V.A.

>>>>

\section{General Response}
We thank all the reviewers for their invaluable comments, which help
us a lot in improving the paper. We believe that the paper is now more
self-contained and better presented than the original submission.

According to the comments, we make some minor revisions, which are
highlighted in the manuscript.  And detailed responses to all the
comments are shown in the rest of this document.

@@

Thanks for your positive comments.

@@

Thank you very much for the approval.

@@

Yes, they are terms as well. This is specified now.

@@

Thanks for the suggestion. Actually some of the timed operators are
used in Section V.A when describing the properties we verify. This
little problem is addressed now. We now only mention the necessary
timed operators which will be used, and also add explanations when
using them in Section V.A.
